\chapter*{Acknowledgements}


The completion of this project was not a solitary endeavor, but a challenging and rewarding journey made possible only by the unwavering support, guidance, and encouragement of many brilliant individuals and organizations. As we reach the finish line, we realize that this work is a reflection not just of our own efforts, but of the collective wisdom and generosity of the community that surrounded us. We would like to extend our deepest and most sincere gratitude to everyone who has walked this path with us.

First and foremost, we are profoundly grateful to our supervisor, Dr. Lê Trọng Nhân. His invaluable insights, deep technical expertise, and critical feedback were indispensable in shaping the direction of our research. Beyond just academic guidance, we thank him for his patience during our moments of uncertainty and for constantly pushing us to refine our thinking. His mentorship taught us to look beyond simple solutions and strive for engineering excellence; we are better engineers today because of his high standards and dedication.

We would also like to express our immense appreciation to PopcornSAR Inc. for providing the essential resources, advanced tools, and professional environment that allowed this project to flourish. It has been a distinct privilege to receive such strong backing from the company’s leadership, bridging the gap between academic theory and industrial application. We wish to convey our deepest respect and special thanks to Mr. Tom (Chae Seung-yueb), CEO of PopcornSAR, and Mr. Jason (Lee Jae-yoon), Sales Engineer. Thank you for trusting us with this opportunity and for your generosity in sharing your time and knowledge. Your continuous mentorship, open communication, and willingness to guide us through complex technical challenges were the driving forces behind our success.

% Furthermore, we must acknowledge the pivotal role played by Bosch Global Software Technologies Vietnam (BGSW Vietnam). Our internship experience there was instrumental in giving us a clear, practical perspective on the automotive software industry. The rigorous foundation we built and the professional standards we learned at BGSW Vietnam were crucial in helping us execute this project effectively. The discipline and industry-standard workflows we absorbed during our time there have become an integral part of our professional identity.

We also wish to extend our thanks to the many unnamed colleagues, lab mates, and peers who offered advice, helped troubleshoot issues, or simply provided moral support when the workload felt heavy. Your camaraderie made the difficult days manageable and the victories sweeter.

Finally, to our families and friends, no words can fully express our thanks. Thank you for your unwavering belief in us, your understanding during our busiest moments, and your endless encouragement when we were exhausted. You have been our anchor, providing the emotional stability we needed to focus on this goal. We dedicate this achievement to you, for you have been with us in spirit every step of the way.

\clearpage
