\chapter*{Declaration}


We, the undersigned students, hereby solemnly declare that this project report entitled \textbf{``Design and Development Driving Automation Software based on Adaptive AUTOSAR Architecture"} represents our original work and has been completed in fulfillment of the requirements for the Computer Engineering Project at Ho Chi Minh City University of Technology, Vietnam National University Ho Chi Minh City.

We affirm with complete integrity that:

\begin{itemize}
    \item This report is the product of our own independent research, analysis, and development efforts under the supervision of Dr. Lê Trọng Nhân.
    
    \item All sources of information, including published works, technical documentation, research papers, online resources, and personal communications, have been properly acknowledged and cited in accordance with academic standards.
    
    \item The software implementation, system design, and experimental results presented in this report are based on our own work and understanding, developed through diligent study and practical application.
    
    \item Where we have used ideas, methodologies, code snippets, or technical approaches from other sources, we have provided appropriate attribution and references.
    
    \item This work has not been previously submitted, either in whole or in part, for any other academic qualification or professional certification at this or any other institution.
    
    \item We accept full responsibility for the accuracy and authenticity of the content presented in this report.
\end{itemize}

We understand that any form of plagiarism, fabrication, or misrepresentation of work constitutes a serious breach of academic integrity and may result in disciplinary action. We have conducted this project with honesty, dedication, and respect for intellectual property rights. We make this declaration with full awareness of its significance and accept all consequences that may arise from any violation of this statement.

% \vspace{12pt}

% \begin{flushright}
% \textit{Ho Chi Minh City, December 2025}

% \vspace{1cm}

% \textbf{Student 1:} \underline{\hspace{4cm}}\\
% \textit{Nguyễn Huy Tài (2110513)}

% \vspace{1cm}

% \textbf{Student 2:} \underline{\hspace{4cm}}\\
% \textit{Nguyễn Đăng Duy (2252116)}
% \end{flushright}

\clearpage
